### 2024-05-15 sections/2-methods.tex
added ceiling on d in complexity bounds

We start with the assumption that the LFD near the query does not differ significantly from that of nearby clusters, and we consider leaf clusters with cardinalities near $k$.
Let $d$ be the LFD in this region.
Then the number of leaf-clusters in $Q$ is bounded above by $2d$, e.g. we could have a cluster overlapping the query ball at each end of each of $d$ mutually-orthogonal axes.
In the worst-case scenario for tree-search, these leaf clusters would all come from different branches of the tree, and so tree-search looks at $2 \cdot d \cdot \log \mathcal{N}_{\hat{r}}(X)$ clusters.
Thus, the asymptotic complexity is

\begin{equation*}
    \mathcal{T} \coloneqq \mathcal{O} \big( d \cdot \log \mathcal{N}_{\hat{r}}(X) \big).
\end{equation*}

>>>>

We start with the assumption that the LFD near the query does not differ significantly from that of nearby clusters, and we consider leaf clusters with cardinalities near $k$.
Let $d$ be the LFD in this region.
Then the number of leaf-clusters in $Q$ is bounded above by $2d$, e.g. we could have a cluster overlapping the query ball at each end of each of $\lceil d \rceil$ mutually-orthogonal axes.
In the worst-case scenario for tree-search, these leaf clusters would all come from different branches of the tree, and so tree-search looks at $2 \cdot \lceil d \rceil \cdot \log \mathcal{N}_{\hat{r}}(X)$ clusters.
Thus, the asymptotic complexity is

\begin{equation*}
    \mathcal{T} \coloneqq \mathcal{O} \big( \lceil d \rceil \cdot \log \mathcal{N}_{\hat{r}}(X) \big).
\end{equation*}

### 2024-05-15 sections/5-discussion.tex
added ceiling on d in complexity bounds

When written with the same notation as used in Section~\ref{sec:methods:knn-search:complexity-of-sieve-methods}, we see that the time complexity of Repeated $\rho$-NN is $\mathcal{O}(\tfrac{\mathcal{T}}{d} + \mathcal{L})$, where $\mathcal{T}$ is the time complexity of tree-search and $\mathcal{L}$ is the time complexity of leaf-search. 
Even though Repeated $\rho$-NN has the lowest time complexity (compare to $\mathcal{O}(\mathcal{T}\log{(\mathcal{T}+\mathcal{L})} + \mathcal{L}\log{(\mathcal{T}+\mathcal{L})})$ for Breadth-First Sieve and $\mathcal{O}(\mathcal{T}\log{\mathcal{T}} + \mathcal{L}\log{k})$ for Depth-First Sieve) of the three CAKES algorithms, it is not always the fastest algorithm empirically. 
We believe that some of this discrepancy can be explained by the fact that if Repeated $\rho$-NN significantly ``overshoots'' the correct radius for $k$ hits ($\rho_k$) during tree-search, leaf-search will require looking at more points, rendering the true scaling factor higher than that in Equation~\ref{eq:methods:repeated-rnn-complexity}.
This overshot can occur when the LFDs of clusters near the query are not concentrated around their expectation. 
For example, if most clusters near the query have very low LFD except for one anomaly with very high LFD, 
the harmonic mean LFD $\mu$ can still be low, so the factor of radial increase~\ref{eq:methods:repeated-rnn-factor} may be much larger than necessary for guaranteeing $k$ hits.  
This suggests that rather than using the reciprocal of the \textit{harmonic} mean LFD in~\ref{eq:methods:repeated-rnn-factor}, we may achieve better results with a mean that is more sensitive to high outliers, such as the geometric mean.
We leave it as an avenue for future work to characterize when Repeated $\rho$-NN significantly ``overshoots'' $\rho_k$ and to improve upon the factor of radial increase in~\ref{eq:methods:repeated-rnn-factor} so that this occurs less frequently and with less severity.

>>>>

When written with the same notation as used in Section~\ref{sec:methods:knn-search:complexity-of-sieve-methods}, we see that the time complexity of Repeated $\rho$-NN is $\mathcal{O}(\tfrac{\mathcal{T}}{\lceil d \rceil} + \mathcal{L})$, where $\mathcal{T}$ is the time complexity of tree-search and $\mathcal{L}$ is the time complexity of leaf-search. 
Even though Repeated $\rho$-NN has the lowest time complexity (compare to $\mathcal{O}(\mathcal{T}\log{(\mathcal{T}+\mathcal{L})} + \mathcal{L}\log{(\mathcal{T}+\mathcal{L})})$ for Breadth-First Sieve and $\mathcal{O}(\mathcal{T}\log{\mathcal{T}} + \mathcal{L}\log{k})$ for Depth-First Sieve) of the three CAKES algorithms, it is not always the fastest algorithm empirically. 
We believe that some of this discrepancy can be explained by the fact that if Repeated $\rho$-NN significantly ``overshoots'' the correct radius for $k$ hits ($\rho_k$) during tree-search, leaf-search will require looking at more points, rendering the true scaling factor higher than that in Equation~\ref{eq:methods:repeated-rnn-complexity}.
This overshot can occur when the LFDs of clusters near the query are not concentrated around their expectation. 
For example, if most clusters near the query have very low LFD except for one anomaly with very high LFD, 
the harmonic mean LFD $\mu$ can still be low, so the factor of radial increase~\ref{eq:methods:repeated-rnn-factor} may be much larger than necessary for guaranteeing $k$ hits.  
This suggests that rather than using the reciprocal of the \textit{harmonic} mean LFD in~\ref{eq:methods:repeated-rnn-factor}, we may achieve better results with a mean that is more sensitive to high outliers, such as the geometric mean.
We leave it as an avenue for future work to characterize when Repeated $\rho$-NN significantly ``overshoots'' $\rho_k$ and to improve upon the factor of radial increase in~\ref{eq:methods:repeated-rnn-factor} so that this occurs less frequently and with less severity.
